A critical re-analysis of six implicit learning papers

### 2022-06-02 docs/manuscript/manuscript.Rmd
update - title change

---
title             : "Data irregularities across six implicit learning articles: Comments on @lola2021b, @lola2021, @lola2020, @tzetzis2015, @lola2012, and @tzetzis2010"

shorttitle        : "Commentary on Lola & Tzetzis papers"

>>>>

---
title             : "A critical re-analysis of six implicit learning papers"

shorttitle        : "Commentary on implicit learning papers"
